Deciding to Disclose

### 2015-06-12 Model.tex
Typos

and by the same method, \(R_{w}(m)=-7\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.

@@

and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-\frac{1}{2}\)) signals, once again concluding that honesty is the better option.

>>>>

and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.

@@

and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
